---
title: "COUNTY DATASET CODE"
author: "Kyle Huisman"
date: "6/10/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{R}
library(tidyverse)
install.packages(lubridate)
```
# below we can use the file=url() function to read directly from github
# notice the dataset ends with ?raw=true
```{R}
county_covid<-read_csv(file=url('https://github.com/nytimes/covid-19-data/blob/master/us-counties.csv?raw=true'))
```

## here's a first cut at calculating monthly  case totals
## Because the csv was imported with the tidyverse read_csv function,
## The dates are already stored in an amenable format.

## I'm not familiar with these commands, but this is what we should use
## https://lubridate.tidyverse.org/

# to make it easier, trying out Michigan first.
```{R}
MI_county<-county_covid %>%
  filter(state=="Michigan")
```

# there are several functions for working with dates.
# just tabulating the cases over months and years, you use
# months() and years() as functions applied to the date column:
```{R}
MI_county %>%
  group_by(year(date), month(date)) %>%
  summarise(sum(cases))
```
# then adding county:
```{R}
MI_county %>%
  group_by(year(date), month(date), county) %>%
  summarise(sum(cases))
```

```{r}
ymd("2020-01-21")
parse_date_time(x= "date", orders="2020-01-21")


```


## We'll have to figure out how to get these monthly counts into an organized dataset



################################### Merging data tables ###################################
## https://dplyr.tidyverse.org/reference/join.html

# once we get the election and census, other data, we'll need to merge them together.
# we will do this with 'joins'...


inner_join(data, by="fips") %>%


